fit_crcvm

### 2024-11-08 R/application/CRCVM/fit_crcvm.Rmd
reorganize folders

D_low=0.07
D_up=3
dataBE1[dataBE1$DistanceShore> D_up,"ExpShore"]=0
dataBE1[dataBE1$DistanceShore< D_low,"ExpShore"]=1/D_low

@@

#model formula
formulas <- list(mu1=~1,mu2=~1,tau =~1,nu=~1,omega=~1)

# Fit baseline with 35m measurement error
sigma_obs=0.035
H=array(rep(sigma_obs^2*diag(2),n_pre),dim=c(2,2,n_pre))

baseline0_35m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",response = c("x","y"),
                    par0 = par0,other_data=list("H"=H),fixpar=c("mu1","mu2"))
baseline0_35m$fit()

@@

```{r results baseline0}
estimates_bas0_35m=as.list(baseline0_35m$tmb_rep(),what="Est")
std_bas0_35m=as.list(baseline0_35m$tmb_rep(),what="Std")

@@

#initial parameters
par0 <- c(0,0,1,4,0)
init_lambda=c(1/0.2^2,1/0.2^2,0.01)

#model formula
formulas <- list(mu1=~1,mu2=~1,
                 tau =~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),
                 omega=~s(AngleNormal,k=5,bs="cs"))

# Fit baseline with 35m measurement error
sigma_obs=0.035
H=array(rep(sigma_obs^2*diag(2),n_pre),dim=c(2,2,n_pre))

baseline1_35m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",response = c("x","y"),
                    par0 = par0,other_data=list("H"=H),fixpar=c("mu1","mu2"),
                    map=list(log_lambda=factor(c("tau.s(ID)","nu.s(ID)",NA))))

baseline1_35m$update_lambda(init_lambda)

baseline1_35m$fit()

@@

baseline1_50m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",response = c("x","y"),
                    par0 = par0,other_data=list("H"=H),fixpar=c("mu1","mu2"),
                    map=list(log_lambda=factor(c("tau.s(ID)","nu.s(ID)",NA))))

@@

@@

baseline1_75m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",response = c("x","y"),
                    par0 = par0,other_data=list("H"=H),fixpar=c("mu1","mu2"),
                    map=list(log_lambda=factor(c("tau.s(ID)","nu.s(ID)",NA))))

@@

@@

baseline1_100m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",response = c("x","y"),
                    par0 = par0,other_data=list("H"=H),fixpar=c("mu1","mu2"),
                    map=list(log_lambda=factor(c("tau.s(ID)","nu.s(ID)",NA))))

@@

@@

```{r results baseline1}
estimates_bas1_35m=as.list(baseline1_35m$tmb_rep(),what="Est")
std_bas1_35m=as.list(baseline1_35m$tmb_rep(),what="Std")

@@

plots_bas1_35m=baseline1_35m$get_all_plots(baseline=NULL,model_name="baseline1_35m",show_CI="pointwise",save=TRUE)
plots_bas1_50m=baseline1_50m$get_all_plots(baseline=NULL,model_name="baseline1_50m",show_CI="pointwise",save=TRUE)
plots_bas1_75m=baseline1_75m$get_all_plots(baseline=NULL,model_name="baseline1_75m",show_CI="pointwise",save=TRUE)
plots_bas1_100m=baseline1_100m$get_all_plots(baseline=NULL,model_name="baseline1_100m",show_CI="pointwise",save=TRUE)

@@

@@

#initial parameters
par0 <- c(0,0,1,4,0)
init_lambda=c(1/0.2^2,1/0.2^2,1,0.01,1,1)

formulas <- list(mu1 = ~1 ,mu2 =~1,tau =~s(ID,bs="re"),nu=~s(ID,bs="re"),
                 omega=~ti(DistanceShore,k=5,bs="cs")+ti(AngleNormal,k=5,bs="cs")+ti(AngleNormal,DistanceShore,k=c(5,5),bs="cs"))

# Fit baseline with 35m measurement error
sigma_obs=0.035
H=array(rep(sigma_obs^2*diag(2),n_pre),dim=c(2,2,n_pre))

baseline2_35m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("H"=H),
                    fixpar=c("mu1","mu2"),map=list("log_lambda"=factor(c(1,2,rep(NA,4)))))

baseline2_35m$update_lambda(init_lambda)
baseline2_35m$fit()

@@

baseline2_50m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("H"=H),
                    fixpar=c("mu1","mu2"),map=list("log_lambda"=factor(c(1,2,rep(NA,4)))))

baseline2_50m$update_lambda(init_lambda)
baseline2_50m$fit()

@@

baseline2_75m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("H"=H),
                    fixpar=c("mu1","mu2"),map=list("log_lambda"=factor(c(1,2,rep(NA,4)))))

baseline2_75m$update_lambda(init_lambda)
baseline2_75m$fit()

@@

baseline2_100m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("H"=H),
                    fixpar=c("mu1","mu2"),map=list("log_lambda"=factor(c(1,2,rep(NA,4)))))

baseline2_100m$update_lambda(init_lambda)
baseline2_100m$fit()

@@

estimates_bas2_35m=as.list(baseline2_35m$tmb_rep(),what="Est")
std_bas2_35m=as.list(baseline2_35m$tmb_rep(),what="Std")

@@

xmin=list("DistanceShore"=0.07)
xmax=list("DistanceShore"=5)

plots_bas2_35m=baseline2_35m$get_all_plots(baseline=NULL,model_name="baseline2_35m",xmin=xmin,xmax=xmax,show_CI="pointwise",save=TRUE)
plots_bas2_50m=baseline2_50m$get_all_plots(baseline=NULL,model_name="baseline2_50m",xmin=xmin,xmax=xmax,show_CI="pointwise",save=TRUE)
plots_bas2_75m=baseline2_75m$get_all_plots(baseline=NULL,model_name="baseline2_75m",xmin=xmin,xmax=xmax,show_CI="pointwise",save=TRUE)
plots_bas2_100m=baseline2_100m$get_all_plots(baseline=NULL,model_name="baseline2_100m",xmin=xmin,xmax=xmax,show_CI="pointwise",save=TRUE)
```

@@

post_coeff_bas2_35m=baseline2_35m$post_coeff(n_post=1000)
post_par_bas2_35m=list("tau0"=exp(post_coeff_bas2_35m$coeff_fe[,"tau.(Intercept)"]),
              "nu0"=exp(post_coeff_bas2_35m$coeff_fe[,"nu.(Intercept)"]),
              "omega0"=post_coeff_bas2_35m$coeff_fe[,"omega.(Intercept)"],
              "sigma_tau"=1/sqrt(exp(post_coeff_bas2_35m$log_lambda[,1])),
              "sigma_nu"=1/sqrt(exp(post_coeff_bas2_35m$log_lambda[,2])))
mean_par_bas2_35m=lapply(post_par_bas2_35m,mean)
sd_par_bas2_35m=lapply(post_par_bas2_35m,sd)

@@

#initial parameters
par0 <- c(0,0,1,4,0)
init_lambda=c(1,1,0.01,1,1,1)

formulas <- list(mu1 = ~1 ,mu2 =~1,tau =~s(ID,bs="re"),nu=~s(ID,bs="re"),
                   omega=~ti(AngleNormal,k=5,bs="cs")+ti(ExpShore,k=5,bs="cs")+ti(AngleNormal,ExpShore,k=c(5,5),bs="cs"))

# Fit baseline with 35m measurement error
sigma_obs=0.035
H=array(rep(sigma_obs^2*diag(2),n_pre),dim=c(2,2,n_pre))

baseline3_35m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("H"=H),
                    fixpar=c("mu1","mu2"),map=list("log_lambda"=factor(c(1,2,rep(NA,4)))))

baseline3_35m$update_lambda(init_lambda)
baseline3_35m$fit()

@@

baseline3_50m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("H"=H),
                    fixpar=c("mu1","mu2"),map=list("log_lambda"=factor(c(1,2,rep(NA,4)))))

baseline3_50m$update_lambda(init_lambda)
baseline3_50m$fit()

@@

baseline3_75m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("H"=H),
                    fixpar=c("mu1","mu2"),map=list("log_lambda"=factor(c(1,2,rep(NA,4)))))

baseline3_75m$update_lambda(init_lambda)
baseline3_75m$fit()

@@

baseline3_100m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("H"=H),
                    fixpar=c("mu1","mu2"),map=list("log_lambda"=factor(c(1,2,rep(NA,4)))))

baseline3_100m$update_lambda(init_lambda)
baseline3_100m$fit()
```
```{r get results baseline3}

estimates_bas3_35m=as.list(baseline3_35m$tmb_rep(),what="Est")
std_bas3_35m=as.list(baseline3_35m$tmb_rep(),what="Std")

@@

plots_bas3_35m=baseline3_35m$get_all_plots(baseline=NULL,model_name="baseline3_35m",
                            xmin=xmin,xmax=xmax,link=link,xlabel=xlabel,show_CI="pointwise",save=TRUE)

plots_bas3_50m=baseline3_50m$get_all_plots(baseline=NULL,model_name="baseline3_50m",
                            xmin=xmin,xmax=xmax,link=link,xlabel=xlabel,show_CI="pointwise",save=TRUE)

plots_bas3_75m=baseline3_75m$get_all_plots(baseline=NULL,model_name="baseline3_75m",
                            xmin=xmin,xmax=xmax,link=link,xlabel=xlabel,show_CI="pointwise",save=TRUE)

plots_bas3_100m=baseline3_100m$get_all_plots(baseline=NULL,model_name="baseline3_100m",
                            xmin=xmin,xmax=xmax,link=link,xlabel=xlabel,show_CI="pointwise",save=TRUE)

@@

@@

post_coeff_bas3_35m=baseline3_35m$post_coeff(n_post=1000)
post_par_bas3_35m=list("tau0"=exp(post_coeff_bas3_35m$coeff_fe[,"tau.(Intercept)"]),
              "nu0"=exp(post_coeff_bas3_35m$coeff_fe[,"nu.(Intercept)"]),
              "omega0"=post_coeff_bas3_35m$coeff_fe[,"omega.(Intercept)"],
              "sigma_tau"=1/sqrt(exp(post_coeff_bas3_35m$log_lambda[,1])),
              "sigma_nu"=1/sqrt(exp(post_coeff_bas3_35m$log_lambda[,2])))
mean_par_bas3_35m=lapply(post_par_bas3_35m,mean)
sd_par_bas3_35m=lapply(post_par_bas3_35m,sd)

post_coeff_bas3_50m=baseline3_50m$post_coeff(n_post=1000)
post_par_bas3_50m=list("tau0"=exp(post_coeff_bas3_50m$coeff_fe[,"tau.(Intercept)"]),
              "nu0"=exp(post_coeff_bas3_50m$coeff_fe[,"nu.(Intercept)"]),
              "omega0"=post_coeff_bas3_50m$coeff_fe[,"omega.(Intercept)"],
              "sigma_tau"=1/sqrt(exp(post_coeff_bas3_50m$log_lambda[,1])),
              "sigma_nu"=1/sqrt(exp(post_coeff_bas3_50m$log_lambda[,2])))
mean_par_bas3_50m=lapply(post_par_bas3_50m,mean)
sd_par_bas3_50m=lapply(post_par_bas3_50m,sd)

post_coeff_bas3_75m=baseline3_75m$post_coeff(n_post=1000)
post_par_bas3_75m=list("tau0"=exp(post_coeff_bas3_75m$coeff_fe[,"tau.(Intercept)"]),
              "nu0"=exp(post_coeff_bas3_75m$coeff_fe[,"nu.(Intercept)"]),
              "omega0"=post_coeff_bas3_75m$coeff_fe[,"omega.(Intercept)"],
              "sigma_tau"=1/sqrt(exp(post_coeff_bas3_75m$log_lambda[,1])),
              "sigma_nu"=1/sqrt(exp(post_coeff_bas3_75m$log_lambda[,2])))
mean_par_bas3_75m=lapply(post_par_bas3_75m,mean)
sd_par_bas3_75m=lapply(post_par_bas3_75m,sd)

post_coeff_bas3_100m=baseline3_100m$post_coeff(n_post=1000)
post_par_bas3_100m=list("tau0"=exp(post_coeff_bas3_100m$coeff_fe[,"tau.(Intercept)"]),
              "nu0"=exp(post_coeff_bas3_100m$coeff_fe[,"nu.(Intercept)"]),
              "omega0"=post_coeff_bas3_100m$coeff_fe[,"omega.(Intercept)"],
              "sigma_tau"=1/sqrt(exp(post_coeff_bas3_100m$log_lambda[,1])),
              "sigma_nu"=1/sqrt(exp(post_coeff_bas3_100m$log_lambda[,2])))
mean_par_bas3_100m=lapply(post_par_bas3_100m,mean)
sd_par_bas3_100m=lapply(post_par_bas3_100m,sd)

@@

```{r smooth omega baseline3}

plot1=plots_bas3_50m$fe_omega_AngleNormal_q1_ExpShore
plot2=plots_bas3_50m$fe_omega_AngleNormal_q2_ExpShore
plot4=plots_bas3_50m$fe_omega_AngleNormal_q4_ExpShore

@@

estimates_res1_sp_35m=as.list(response1_sp_35m$tmb_rep(),what="Est")
std_res1_sp_35m=as.list(response1_sp_35m$tmb_rep(),what="Std")

@@

```{r estimates on parameter scale response1}

>>>>

D_low=0.073
D_up=3
dataBE1[dataBE1$DistanceShore> D_up,"ExpShore"]=0
dataBE1[dataBE1$DistanceShore< D_low,"ExpShore"]=1/D_low

@@

#model formula
formulas <- list(mu1=~1,mu2=~1,tau =~s(ID,bs="re"),nu=~s(ID,bs="re"),omega=~1)

# Fit baseline 
baseline0<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",response = c("x","y"),
                    par0 = par0,other_data=list("log_sigma_obs0"=log(0.05)),fixpar=c("mu1","mu2"))
baseline0$fit()

# Fit baseline with fixed 25m measurement error
sigma_obs=0.025
H=array(rep(sigma_obs^2*diag(2),n_pre),dim=c(2,2,n_pre))

baseline0_25m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",response = c("x","y"),
                    par0 = par0,other_data=list("H"=H),fixpar=c("mu1","mu2"))
baseline0_25m$fit()

@@

```{r results baseline0}

estimates_bas0=as.list(baseline0$tmb_rep(),what="Est")
std_bas0=as.list(baseline0$tmb_rep(),what="Std")

estimates_bas0_25m=as.list(baseline0_25m$tmb_rep(),what="Est")
std_bas0_25m=as.list(baseline0_25m$tmb_rep(),what="Std")

@@

#initial parameters
par0 <- c(0,0,1,4,0)
init_lambda=c(1,1,1)

#model formula
formulas <- list(mu1=~1,mu2=~1,
                 tau =~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),
                 omega=~s(AngleNormal,k=5,bs="cp"))

# Fit baseline 
baseline1<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",response = c("x","y"),
                    par0 = par0,other_data=list("log_sigma_obs0"=log(0.05)),fixpar=c("mu1","mu2"))

baseline1$update_map(new_map=list(log_lambda=factor(c("tau.s(ID)","nu.s(ID)",NA))))
baseline1$fit()

@@

baseline1_50m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",response = c("x","y"),
                    par0 = par0,other_data=list("H"=H),fixpar=c("mu1","mu2"))

@@

baseline1_50m$update_map(new_map=list(log_lambda=factor(c("tau.s(ID)","nu.s(ID)",NA))))

@@

baseline1_75m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",response = c("x","y"),
                    par0 = par0,other_data=list("H"=H),fixpar=c("mu1","mu2"))

@@

baseline1_75m$update_map(new_map=list(log_lambda=factor(c("tau.s(ID)","nu.s(ID)",NA))))

@@

baseline1_100m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",response = c("x","y"),
                    par0 = par0,other_data=list("H"=H),fixpar=c("mu1","mu2"))

@@

baseline1_100m$update_map(new_map=list(log_lambda=factor(c("tau.s(ID)","nu.s(ID)",NA))))

@@

```{r results baseline1}

#get estimates
estimates_bas1=as.list(baseline1$tmb_rep(),what="Est")
std_bas1=as.list(baseline1$tmb_rep(),what="Std")

@@

#get plots

plots_bas1=baseline1$get_all_plots(baseline=NULL,show_CI="simultaneous")
plots_bas1_50m=baseline1_50m$get_all_plots(baseline=NULL,show_CI="pointwise")
plots_bas1_75m=baseline1_75m$get_all_plots(baseline=NULL,show_CI="pointwise")
plots_bas1_100m=baseline1_100m$get_all_plots(baseline=NULL,show_CI="pointwise")

@@

```{r display plots baseline1}

plots_bas1
plots_bas1_50m
plots_bas1_75m
plots_bas1_100m
```

@@

#initial parameters
par0 <- c(0,0,1,4,0)
init_lambda=c(1,1,0.1,1,1,1)

formulas <- list(mu1 = ~1 ,mu2 =~1,tau =~s(ID,bs="re"),nu=~s(ID,bs="re"),
                 omega=~ti(DistanceShore,k=5,bs="cs")+ti(AngleNormal,k=5,bs="cp")+ti(AngleNormal,DistanceShore,k=c(5,5),bs="cs"))

# Fit baseline 
baseline2<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",response = c("x","y"),
                    par0 = par0,other_data=list("log_sigma_obs0"=log(0.035)),fixpar=c("mu1","mu2"))

baseline2$update_map(new_map=list(log_lambda=factor(c("tau.s(ID)","nu.s(ID)",rep(NA,4)))))
baseline2$fit()

@@

baseline2_50m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("H"=H),
                    fixpar=c("mu1","mu2"))

baseline2_50m$update_lambda(init_lambda)
baseline2_50m$update_map(new_map=list(log_lambda=factor(c("tau.s(ID)","nu.s(ID)",rep(NA,4)))))
baseline2_50m$fit()

@@

baseline2_75m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("H"=H),
                    fixpar=c("mu1","mu2"))

baseline2_75m$update_lambda(init_lambda)
baseline2_75m$update_map(new_map=list(log_lambda=factor(c("tau.s(ID)","nu.s(ID)",rep(NA,4)))))
baseline2_75m$fit()

@@

baseline2_100m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("H"=H),
                    fixpar=c("mu1","mu2"))

baseline2_100m$update_lambda(init_lambda)
baseline2_100m$update_map(new_map=list(log_lambda=factor(c("tau.s(ID)","nu.s(ID)",rep(NA,4)))))
baseline2_100m$fit()

@@

estimates_bas2=as.list(baseline2$tmb_rep(),what="Est")
std_bas2=as.list(baseline2$tmb_rep(),what="Std")

@@

xmin=list("DistanceShore"=0.073)
xmax=list("DistanceShore"=5)

plots_bas2=baseline2$get_all_plots(baseline=NULL,xmin=xmin,xmax=xmax,show_CI="pointwise")

plots_bas2_50m=baseline2_50m$get_all_plots(baseline=NULL,xmin=xmin,xmax=xmax,show_CI="pointwise")
plots_bas2_75m=baseline2_75m$get_all_plots(baseline=NULL,xmin=xmin,xmax=xmax,show_CI="pointwise")
plots_bas2_100m=baseline2_100m$get_all_plots(baseline=NULL,xmin=xmin,xmax=xmax,show_CI="pointwise")
```

```{r display plots baseline2}

#print plots
plots_bas2
plots_bas2_50m
plots_bas2_75m
plots_bas2_100m

```{r save plots baseline2}
# Create directory
if (!dir.exists("baseline2_50m")) {
    dir.create("baseline2_50m", recursive = TRUE)
}

# Use lapply to save each plot
lapply(seq_along(plots_bas2), function(i) {

    plot<-plots_bas2[[i]]
    plot_name <- names(plots_bas2)[i]
    file_path <- file.path("baseline2_50m", plot_name)

    # Check if the plot is a ggplot or plotly object
    if (inherits(plot, "ggplot")) {
      ggsave(file_path, plot, device = "pdf")
    } else if (inherits(plot, "plotly")) {
      saveWidget(plot, file_path)
  }
    })
```

@@

post_coeff_bas2=baseline2$post_coeff(n_post=1000)
post_par_bas2=list("tau0"=exp(post_coeff_bas2$coeff_fe[,"tau.(Intercept)"]),
              "nu0"=exp(post_coeff_bas2$coeff_fe[,"nu.(Intercept)"]),
              "omega0"=post_coeff_bas2$coeff_fe[,"omega.(Intercept)"],
              "sigma_tau"=1/sqrt(exp(post_coeff_bas2$log_lambda[,1])),
              "sigma_nu"=1/sqrt(exp(post_coeff_bas2$log_lambda[,2])))
mean_par_bas2=lapply(post_par_bas2,mean)
sd_par_bas2=lapply(post_par_bas2,sd)

@@

#initial parameters
par0 <- c(0,0,1,4,0)
init_lambda=c(1,1,1,1,1,1)

#mapping for fixed smooth penalties
new_map=list("log_lambda"=factor(c("tau.s(ID)","nu.s(ID)",rep(NA,4))))

#parameters formulas
formulas <- list(mu1 = ~1 ,mu2 =~1,tau =~s(ID,bs="re"),nu=~s(ID,bs="re"),
                   omega=~ti(AngleNormal,k=5,bs="cs")+ti(ExpShore,k=5,bs="cs")+
                   ti(AngleNormal,ExpShore,k=c(5,5),bs="cs"))

# Fit baseline
baseline3<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("log_sigma_obs0"=log(0.035)),
                    fixpar=c("mu1","mu2"))

baseline3$update_lambda(init_lambda)
baseline3$update_map(new_map)
baseline3$fit()

# Fit baseline with 30m measurement error
sigma_obs=0.03
H=array(rep(sigma_obs^2*diag(2),n_pre),dim=c(2,2,n_pre))

baseline3_30m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("H"=H),
                    fixpar=c("mu1","mu2"))

baseline3_30m$update_lambda(init_lambda)
baseline3$update_map(new_map)
baseline3_30m$fit()

# Fit baseline with 40m measurement error
sigma_obs=0.04
H=array(rep(sigma_obs^2*diag(2),n_pre),dim=c(2,2,n_pre))

baseline3_40m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("H"=H),
                    fixpar=c("mu1","mu2"))

baseline3_40m$update_lambda(init_lambda)
baseline3_40m$update_map(new_map)
baseline3_40m$fit()

# Fit baseline with 45m measurement error
sigma_obs=0.045
H=array(rep(sigma_obs^2*diag(2),n_pre),dim=c(2,2,n_pre))

baseline3_45m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("H"=H),
                    fixpar=c("mu1","mu2"))

baseline3_45m$update_lambda(init_lambda)
baseline3_45m$update_map(new_map)
baseline3_45m$fit()

@@

baseline3_50m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("H"=H),
                    fixpar=c("mu1","mu2"))

baseline3_50m$update_lambda(init_lambda)
baseline3_50m$update_map(new_map)
baseline3_50m$fit()

@@

baseline3_75m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("H"=H),
                    fixpar=c("mu1","mu2"))

baseline3_75m$update_lambda(init_lambda)
baseline3_75m$update_map(new_map)
baseline3_75m$fit()

@@

baseline3_100m<- SDE$new(formulas = formulas,data = dataBE2,type = "RACVM",
                    response = c("x","y"),par0 = par0,other_data=list("H"=H),
                    fixpar=c("mu1","mu2"))

baseline3_100m$update_lambda(init_lambda)
baseline3_100m$update_map(new_map)
baseline3_100m$fit()
```

```{r get results baseline3}

estimates_bas3=as.list(baseline3$tmb_rep(),what="Est")
std_bas3=as.list(baseline3$tmb_rep(),what="Std")

estimates_bas3_30m=as.list(baseline3_30m$tmb_rep(),what="Est")
std_bas3_30m=as.list(baseline3_30m$tmb_rep(),what="Std")

estimates_bas3_40m=as.list(baseline3_40m$tmb_rep(),what="Est")
std_bas3_40m=as.list(baseline3_40m$tmb_rep(),what="Std")

estimates_bas3_45m=as.list(baseline3_45m$tmb_rep(),what="Est")
std_bas3_45m=as.list(baseline3_45m$tmb_rep(),what="Std")

@@

plots_bas3=baseline3$get_all_plots(baseline=NULL,xmin=xmin,
                                   xmax=xmax,link=link,xlabel=xlabel,show_CI="pointwise")

plots_bas3_30m=baseline3_30m$get_all_plots(baseline=NULL,xmin=xmin,xmax=xmax,
                                           link=link,xlabel=xlabel,show_CI="pointwise")

plots_bas3_40m=baseline3_40m$get_all_plots(baseline=NULL,xmin=xmin,xmax=xmax,
                                           link=link,xlabel=xlabel,show_CI="pointwise")

plots_bas3_45m=baseline3_45m$get_all_plots(baseline=NULL,xmin=xmin,xmax=xmax,
                                           link=link,xlabel=xlabel,show_CI="pointwise")

plots_bas3_50m=baseline3_50m$get_all_plots(baseline=NULL,xmin=xmin,xmax=xmax,
                                           link=link,xlabel=xlabel,show_CI="pointwise")

plots_bas3_75m=baseline3_75m$get_all_plots(baseline=NULL,xmin=xmin,xmax=xmax,
                                           link=link,xlabel=xlabel,show_CI="pointwise")

plots_bas3_100m=baseline3_100m$get_all_plots(baseline=NULL,xmin=xmin,xmax=xmax,
                                             link=link,xlabel=xlabel,show_CI="pointwise")

@@

```{r display plots baseline3}

#print plots
plots_bas3
plots_bas3_50m
plots_bas3_75m
plots_bas3_100m

```{r}
# Create directory
if (!dir.exists("baseline3_50m")) {
    dir.create("baseline3_50m", recursive = TRUE)
}

# Use lapply to save each plot
lapply(seq_along(plots_bas2), function(i) {

    plot<-plots_bas2[[i]]
    plot_name <- names(plots_bas2)[i]
    file_path <- file.path("baseline3_50m", plot_name)

    # Check if the plot is a ggplot or plotly object
    if (inherits(plot, "ggplot")) {
      ggsave(file_path, plot, device = "pdf")
    } else if (inherits(plot, "plotly")) {
      saveWidget(plot, file_path)
  }
    })
```

@@

post_coeff_bas3=baseline3$post_coeff(n_post=10000)
post_par_bas3=list("sigma_obs"=exp(post_coeff_bas3$log_sigma_obs),
              "tau0"=exp(post_coeff_bas3$coeff_fe[,"tau.(Intercept)"]),
              "nu0"=exp(post_coeff_bas3$coeff_fe[,"nu.(Intercept)"]),
              "omega0"=post_coeff_bas3$coeff_fe[,"omega.(Intercept)"],
              "sigma_tau"=1/sqrt(exp(post_coeff_bas3$log_lambda[,1])),
              "sigma_nu"=1/sqrt(exp(post_coeff_bas3$log_lambda[,2])))
mean_par_bas3=lapply(post_par_bas3,mean)
sd_par_bas3=lapply(post_par_bas3,sd)
quant_par_bas3 <- lapply(post_par_bas3, quantile, probs = c(0.025, 0.975))

post_coeff_bas3_30m=baseline3_30m$post_coeff(n_post=10000)
post_par_bas3_30m=list("tau0"=exp(post_coeff_bas3_30m$coeff_fe[,"tau.(Intercept)"]),
              "nu0"=exp(post_coeff_bas3_30m$coeff_fe[,"nu.(Intercept)"]),
              "omega0"=post_coeff_bas3_30m$coeff_fe[,"omega.(Intercept)"],
              "sigma_tau"=1/sqrt(exp(post_coeff_bas3_30m$log_lambda[,1])),
              "sigma_nu"=1/sqrt(exp(post_coeff_bas3_30m$log_lambda[,2])))
mean_par_bas3_30m=lapply(post_par_bas3_30m,mean)
sd_par_bas3_30m=lapply(post_par_bas3_30m,sd)
quant_par_bas3_30m <- lapply(post_par_bas3_30m, quantile, probs = c(0.025, 0.975))

post_coeff_bas3_40m=baseline3_40m$post_coeff(n_post=10000)
post_par_bas3_40m=list("tau0"=exp(post_coeff_bas3_40m$coeff_fe[,"tau.(Intercept)"]),
              "nu0"=exp(post_coeff_bas3_40m$coeff_fe[,"nu.(Intercept)"]),
              "omega0"=post_coeff_bas3_40m$coeff_fe[,"omega.(Intercept)"],
              "sigma_tau"=1/sqrt(exp(post_coeff_bas3_40m$log_lambda[,1])),
              "sigma_nu"=1/sqrt(exp(post_coeff_bas3_40m$log_lambda[,2])))
mean_par_bas3_40m=lapply(post_par_bas3_40m,mean)
sd_par_bas3_40m=lapply(post_par_bas3_40m,sd)
quant_par_bas3_40m <- lapply(post_par_bas3_40m, quantile, probs = c(0.025, 0.975))

post_coeff_bas3_45m=baseline3_45m$post_coeff(n_post=10000)
post_par_bas3_45m=list("tau0"=exp(post_coeff_bas3_45m$coeff_fe[,"tau.(Intercept)"]),
              "nu0"=exp(post_coeff_bas3_45m$coeff_fe[,"nu.(Intercept)"]),
              "omega0"=post_coeff_bas3_45m$coeff_fe[,"omega.(Intercept)"],
              "sigma_tau"=1/sqrt(exp(post_coeff_bas3_45m$log_lambda[,1])),
              "sigma_nu"=1/sqrt(exp(post_coeff_bas3_45m$log_lambda[,2])))
mean_par_bas3_45m=lapply(post_par_bas3_45m,mean)
sd_par_bas3_45m=lapply(post_par_bas3_45m,sd)
quant_par_bas3_45m <- lapply(post_par_bas3_45m, quantile, probs = c(0.025, 0.975))

post_coeff_bas3_50m=baseline3_50m$post_coeff(n_post=10000)
post_par_bas3_50m=list("tau0"=exp(post_coeff_bas3_50m$coeff_fe[,"tau.(Intercept)"]),
              "nu0"=exp(post_coeff_bas3_50m$coeff_fe[,"nu.(Intercept)"]),
              "omega0"=post_coeff_bas3_50m$coeff_fe[,"omega.(Intercept)"],
              "sigma_tau"=1/sqrt(exp(post_coeff_bas3_50m$log_lambda[,1])),
              "sigma_nu"=1/sqrt(exp(post_coeff_bas3_50m$log_lambda[,2])))
mean_par_bas3_50m=lapply(post_par_bas3_50m,mean)
sd_par_bas3_50m=lapply(post_par_bas3_50m,sd)
quant_par_bas3_50m <- lapply(post_par_bas3_50m, quantile, probs = c(0.025, 0.975))

post_coeff_bas3_75m=baseline3_75m$post_coeff(n_post=10000)
post_par_bas3_75m=list("tau0"=exp(post_coeff_bas3_75m$coeff_fe[,"tau.(Intercept)"]),
              "nu0"=exp(post_coeff_bas3_75m$coeff_fe[,"nu.(Intercept)"]),
              "omega0"=post_coeff_bas3_75m$coeff_fe[,"omega.(Intercept)"],
              "sigma_tau"=1/sqrt(exp(post_coeff_bas3_75m$log_lambda[,1])),
              "sigma_nu"=1/sqrt(exp(post_coeff_bas3_75m$log_lambda[,2])))
mean_par_bas3_75m=lapply(post_par_bas3_75m,mean)
sd_par_bas3_75m=lapply(post_par_bas3_75m,sd)
quant_par_bas3_75m <- lapply(post_par_bas3_75m, quantile, probs = c(0.025, 0.975))

post_coeff_bas3_100m=baseline3_100m$post_coeff(n_post=10000)
post_par_bas3_100m=list("tau0"=exp(post_coeff_bas3_100m$coeff_fe[,"tau.(Intercept)"]),
              "nu0"=exp(post_coeff_bas3_100m$coeff_fe[,"nu.(Intercept)"]),
              "omega0"=post_coeff_bas3_100m$coeff_fe[,"omega.(Intercept)"],
              "sigma_tau"=1/sqrt(exp(post_coeff_bas3_100m$log_lambda[,1])),
              "sigma_nu"=1/sqrt(exp(post_coeff_bas3_100m$log_lambda[,2])))
mean_par_bas3_100m=lapply(post_par_bas3_100m,mean)
sd_par_bas3_100m=lapply(post_par_bas3_100m,sd)
quant_par_bas3_100m <- lapply(post_par_bas3_100m, quantile, probs = c(0.025, 0.975))

@@

```{r smooth omega baseline3}
plot1=plots_bas3_50m$fe_omega_AngleNormal_q1_ExpShore
plot2=plots_bas3_50m$fe_omega_AngleNormal_q2_ExpShore
plot4=plots_bas3_50m$fe_omega_AngleNormal_q4_ExpShore

@@

estimates_res1_sp=as.list(response1_sp$tmb_rep(),what="Est")
std_res1_sp=as.list(response1_sp$tmb_rep(),what="Std")

@@

```{r display plots response1_sp}

#print plots
plots_res1_sp
plots_res1_sp_50m
plots_res1_sp_75m
plots_res1_sp_100m
